Illusion Sensitivity and Phenomenological Control

### 2025-05-20 analysis/1_cleaning.qmd
minor changes to scripts

>>>>

### PCS scale score

**Note:** Mean subjective scale responses for item 4 (Taste) and item 10 (Post-session suggestion) are each generated from the combination of two responses which require processing prior to generating an overall subjective score. 
The subjective score for item 4 is the mean of the responses to the (a)‘sour’ and (b)‘sweet’ sub-scales for the taste suggestion. 
The subjective score for item 10 is the geometric mean (the square root of the product) of he responses to the (a) ‘urge’ and (b) ‘amnesia’ sub-scales for the post-session suggestion.

```{r}
data_ppt$pcs_tastescore <- rowMeans(data_ppt[grepl("taste", names(data_ppt))])
data_ppt$pcs_postsessionsuggetsion <- sqrt(data_ppt$pcs_urgepress * data_ppt$pcs_memorypress)
data_ppt$pcs <- rowMeans(data_ppt[, c("pcs_handslow", "pcs_mosquito", "pcs_magnetichands", "pcs_armrigidity", "pcs_tastescore", "pcs_postsessionsuggetsion", "pcs_armimmobile", "pcs_music", "pcs_negativehallucination", "pcs_amnesia")], na.rm = TRUE)
data_ppt$pcs_SD <- sd(data_ppt$pcs, na.rm = TRUE)

### PCS Reliability

pcs_rel <- data_ppt |>
  select("pcs_handslow", "pcs_mosquito", "pcs_magnetichands", "pcs_armrigidity", "pcs_tastescore", "pcs_postsessionsuggetsion", "pcs_armimmobile", "pcs_music", "pcs_negativehallucination", "pcs_amnesia") |>
  psych::alpha()
